Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}

### 2017-03-26 ident_manu.Rnw
figures say collinearity instead of identifiability

% identifiability plot
<<identplo, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \\ac{do} was sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)

@@

% identifiability plot, all state variables
<<identploall, eval = T, fig.cap = 'Average identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for all state variables.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.  The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=

@@

grid.arrange(
  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
  left = 'Identifiability',
  pleg, ncol = 2, widths = c(1, 0.2)
)

@@

% parameter exclusion temp
<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \\cref{fig:identplo}. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "0.8\\textwidth">>=
data(cat_ident_all)

@@

ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
  facet_wrap(~parm, label = label_parsed, ncol = 2) + 
  theme_minimal() + 
  scale_fill_brewer(palette = 'Spectral') + 
  scale_y_continuous('Identifiability', trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +
  scale_x_discrete('Parameters in set') + 
  theme(
    legend.title = element_blank(),
    axis.line.x = element_line(),
    axis.line.y = element_line(),
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(), 
    legend.position = 'top', #c(0.8, 0.1),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm")
  )

>>>>

% identifiability plot
<<identplo, eval = T, fig.cap = 'Collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) of parameter subsets for \\ac{do}.  Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.  Lines represent collinearity ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \\ac{do} was sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 7, fig.width = 8, echo = F, cache = TRUE>>=

@@

leftlab <- expression(paste('Collinearity, ', italic(gamma)))
grid.arrange(
  arrangeGrob(p1, p2, ncol = 2),
  left = textGrob(leftlab, rot = 90),
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)

@@

% identifiability plot, all state variables
<<identploall, eval = T, fig.cap = 'Average collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) of parameter subsets for all state variables.  Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.  Collinearity was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.  The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\\gamma = 1$).', fig.height = 8, fig.width = 9, echo = F, cache = TRUE>>=

@@

leftlab <- expression(paste('Collinearity, ', italic(gamma)))
grid.arrange(
  arrangeGrob(p1, p2, ncol = 2, bottom = 'Parameters in set'),
  left = textGrob(leftlab, rot = 90),
  pleg, ncol = 2, widths = c(1, 0.2)
)

@@

% parameter exclusion temp
<<exclex, eval = T, fig.cap = 'Collinearity ($\\gamma$ as a measure of identifiability, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.  Collinearity is evaluated for subsets that excluded and included the parameters at the top of each plot. Collinearity of including all eight parameters is in \\cref{fig:identplo}. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable collinearity.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "0.8\\textwidth">>=
data(cat_ident_all)

@@

leftlab <- expression(paste('Collinearity, ', italic(gamma)))
ggplot(toplo, aes(x = N, y = coll, fill = inc)) + 
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  geom_boxplot(outlier.size = 0.5, size = 0.5) + 
  facet_wrap(~parm, label = label_parsed, ncol = 2) + 
  theme_minimal() + 
  scale_fill_brewer(palette = 'Spectral') + 
  scale_y_continuous(leftlab, trans = 'log', breaks = c(0.1, 1, 10, 100, 1000)) +
  scale_x_discrete('Parameters in set') + 
  theme(
    legend.title = element_blank(),
    axis.line.x = element_line(),
    axis.line.y = element_line(),
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank(), 
    legend.position = 'top', #c(0.8, 0.1),
    axis.ticks.x = element_line(),
    axis.ticks.y = element_line(),
    axis.ticks.length = unit(.1, "cm")
  )

### 2017-03-26 ident_manu.tex
figures say collinearity instead of identifiability

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Sun Mar 26 14:18:02 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}{4a9eb06d6e3839b6a43aa6e1e4dfe01a06a56524}}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identplo}
\end{figure}

@@

\caption[Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables]{Average identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for all state variables.  Plots in (a) show identifiability by parameter categories and (b) shows identifiability by selecting the top 1 through 4 parameters in all categories.  Identifiability was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.  The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identploall}
\end{figure}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \cref{fig:identplo}. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
\end{figure}

>>>>

\title{Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Version: Sun Mar 26 15:18:56 2017 -0500, \href{https://github.com/fawda123/identifiability/commit/bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}{bf9e2162ec0d9ba7edf4ddc5b7ba5c1019142186}}

@@

\caption{Collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for \ac{do}.  Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.  Lines represent collinearity ranges for the possible combinations given the number of parameters in the set.  The temperature category is not shown because \ac{do} was sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identplo}
\end{figure}

@@

\caption[Average collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for all state variables]{Average collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) of parameter subsets for all state variables.  Plots in (a) show collinearity by parameter categories and (b) shows collinearity by selecting the top 1 through 4 parameters in all categories.  Collinearity was averaged for all combinations in a parameter set to evaluate relative differenes between state variables.  The temperature category is not shown because all state variables were sensitive to only one parameter (i.e., $\gamma = 1$).}\label{fig:identploall}
\end{figure}

@@

\caption{Collinearity ($\gamma$ as a measure of identifiability, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.  Collinearity is evaluated for subsets that excluded and included the parameters at the top of each plot. Collinearity of including all eight parameters is in \cref{fig:identplo}. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable collinearity.}\label{fig:exclex}
\end{figure}
